### 2011-04-04 Spatial_adaptation/standing-variation.tex
/* Standing variation */ random delay notes added

>>>>

\subsection{On the random delay}

Let $Y_t$ be the total number of offspring coming from a single individual
(in the spatial, density-regulated model).
Then we know that $(Y_t/t)^{1/d} \to v$, 
but we saw from simulations that it looked like $Y_t^{1/d} \approx v(t-\tau)$,
where $\tau$ is the (random) establishment time.
(It would be useful to look at the coefficient of variation of $\tau$.)
Well, we know that at first, $Y_t \approx W e^{rt}$, 
where $W= \lim e^{-rt} Z_t$, and $Z_t$ is the associated branching process,
and $r$ is the growth rate (er, $r=s$?).
And eventually, $\partial_t Y_t^{1/d} \approx v$.
If this switchover happened at a fixed size $C$,
the size at which wavelike behavior took over,
i.e.\ when $W e^{rt} = C$,
then for $\tau = \frac{1}{r}\log(C/W)$ we'd have 
\[
    Y_t = \begin{cases}
        W e^{rt} \quad & t \le \tau \\
        (v (t-\tau))^d + C \quad & t > \tau ,
\]
which if $C$ is small relative to the scale we look on will look as described above.
So the random delay is $(1/r)\log(C/W)$; and so the mean delay is something like $(1/r)\log C$
and the randomness is determined by $(1/r)\log W$.
